Reaction Time analysis
========================================================
  ```{rsetup, echo=FALSE, cache=FALSE}
## numbers >= 10^5 will be denoted in scientific notation,
## and rounded to 2 digits
options(scipen = 1, digits = 4)
```

## Introduction     
This fourth analysis is related to a new training script.  

```{recho=FALSE,}
library(ggplot2)
graphics.off()
t=read.csv2("../rawDatas/reactionTimes.csv",sep=";",colClasses=c("factor","numeric","numeric","numeric","factor","factor","numeric","numeric","numeric"),dec=".")
outlierFilter=t$time<5
t=t[outlierFilter,]
means.t=tapply(t$time,t$item, mean)
hist(means.t)
vari=var(t$time)
mean=mean(t$time)
outlierBound=mean+2*sqrt(vari)
outlierFilter1=(t$time<outlierBound)&(t$time>0.45)
t=t[outlierFilter1,]
means.t=tapply(t$time,t$item, mean)
var.t=tapply(t$time,t$item, var)
```
## analysis after outliers filtering

### before the new script
```{r}
n=3
means.first3=tapply(t$time,t$item, function(i) mean(head(i, n)))
sort(means.first3)
m=mean(means.first3)
s=var(means.first3)
m
```
At the begginning we had a mean of `r m` s. and a var of `r s`
### after the new script
```{r}
n=3
means.tlast3=tapply(t$time,t$item, function(i) mean(tail(i, n)))
sort(means.tlast3)
m2=mean(means.tlast3)
s2=var(means.tlast3)
m2
```
After the script we had a mean of `r m2` s. and a var of `r s2`
## Conclusions
In `r nrow(t)` trials a diminishing of `r m-m2` s has been observed, which is consistent with the outcomes of the previous training scripts. More importantly, the variance has been reduced almost by half ( `r 100*((s-s2)/s)` % ).
### Box plots
```{r}
boxplot(cbind(means.first3,means.tlast3))
stripchart(means.first3, 
           vertical = TRUE, method = "jitter", 
           pch = 21, col = "blue", bg = "bisque",
           add = TRUE) 

stripchart(means.tlast3, 
           vertical = TRUE, method = "jitter", 
           pch = 21, col = "red", bg = "bisque",
           add = TRUE,at=2) 
```
